Identifying stellar clusters in chemical-abundance space

### 2016-01-12 papers/clusters.tex
outline

Hello World!!

>>>>

\section{Introduction}

DWH: Chemical tagging yada yada (CITE).

DWH: Open clusters look one-metal (CITE); globulars look peculiar (CITE); but no-one has ever gone the other way!

DWH: Fast intro to \apogee.

DWH: Fast intro to \thecannon.

DWH: BASH the \apogee\ discontiguous field positioning.

\section{Data and method}

MKN: Details about \apogee\ data.

AC: Details about \thecannon\ and implementation.

DWH: Figure showing the full data set; discuss structure.

DWH: Clustering methodology.

\section{Results and discussion}

DWH: For the first time, we see small-scale informative features in abundance space.

DWH: When we identify the small-scale features in abundance space, they are informative in position space.

DWH: How do we show that we aren't just getting clusters because \apogee\ has plate-to-plate calibration variations?

DWH: Chemical tagging will work.

\acknowledgements
DWH: It is a pleasure to thank...

DWH: github repo and hash.

DWH: Be sure to cite software a la the new ApJ guidelines.
